proportion_of_importance_per_annotation

### 2019-08-26 Scripts/proportion_of_importance_per_annotation.Rmd
edits for 5kb results
changed css to chromhmm; added a and b

all_propimp <- rbind(all_propimp_gm12878_summ, all_propimp_K562_summ)
all_propimp$CL <- c(rep("GM12878", 12),
                    rep("K562", 12))

>>>>

all_propimp <- rbind(all_propimp_gm12878_summ, all_propimp_K562_summ)
all_propimp$CL <- c(rep("GM12878", 15),
                    rep("K562", 15))
levels(all_propimp$Annotation) <- c("ChromHMM", "HM", "TFBS")
all_propimp$Annotation <- factor(all_propimp$Annotation, levels=c("HM", "ChromHMM", "TFBS"))
